---
title: "homework-1"
author: "Douglas Zickuhr"
date: "16/10/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r lib load}
library(foreign)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Open the data and make sure that the command for doing so is in the command file.
```{r reading dataset}
df <- read.dta("/Users/dzickuhr/Downloads/DomPolHIrep.dta")
```

# 2. Select only those cases where the value for the votebill variable is equal to “106S98"
```{r filtering}
df_106S98 <- df[df$votebill == "106S98",]
head(df_106S98)
```

# 3. First, we will investigate the relationship between party membership and being a veteran.

## a. Produce a pie chart of the Veteran variable and interpret in one or two sentences. This variable is coded as 1 for veterans and 0 otherwise.
```{r}
pie(table(df$Veteran),
    labels = c("Others","Veterans"))
```

## b. Produce a cross table of whether Democrats are more or less likely than Republicans to be veterans. Party preference is encoded in the party variable, where 100 represents Democrats and 200 Republicans.
```{r}
prop.table(table(df_106S98$party,df_106S98$Veteran,
                 dnn = c("Party","Veterans?")))
```


# 4. Next we will look at the relationship between gender and ideology, where we make use of the so-called NOMINATE scores (Poole and Rosenthal, 1997; Hildebrandt, Hillebrecht and Holm, 2013, 256–257), which are captured in the ideology variable in the data set. As is stated in Hildebrandt, Hillebrecht and Holm (2013, fn. 9): “As a point of reference, George W. Bush’s NOMINATE score is 0.9; Barack Obama’s is -0.4.”

## a. Produce a boxplot of the ideology variable and interpret the distribution of the variable.
```{r}
boxplot(df_106S98$ideology)
```

## b. Produce a histogram of the ideology variable and interpret the distribution.
```{r}
hist(df_106S98$ideology)
```

## c. Calculate the mean, median, variance and standard deviation of the ideology variable.
```{r}
mean(df_106S98$ideology)
```

```{r}
median(df_106S98$ideology)
```

```{r}
var(df_106S98$ideology)
```

```{r}
sd(df_106S98$ideology)
```


## e. Produce a graph with two boxplots, side-by-side, to investigate the relation- ship between Gender and ideology. What do you conclude?
```{r}
boxplot(ideology~Gender,
        data = df_106S98,
        xlab = "Gender",
        ylab = "NOMINATE score")
```



