---
title: "Introduction to R"
author: "Douglas Zickuhr"
date: "11/09/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Atomic Vectors
* boolean
* integer
* double
* character
* complex and raw you won't see very often

```{r atomic vectors}
# Every variable is a vector in R, even when it just a single number
num_vec <- 1
class(num_vec)
mode(num_vec)
typeof(num_vec)
length(num_vec)

# Boolean are just TRUE or FALSE - even though you can have NA which is the absense of value
bool_vec <- c(FALSE,TRUE,TRUE,NA)
bool_vec
class(bool_vec)
mode(bool_vec)
length(bool_vec)

# It is possible to create vectors using functions like seq or rep
num_vec_seq <- seq(1:50)
num_vec_rep <- rep(seq(1:5),10)
set.seed(42)
num_vec_ran <- round(runif(50,0,100),0)

# Characters vectors are very common as well
char_vec <- c("douglas","dublin","1234")
class(char_vec)
```

## Non-atomic vectors
* Lists
```{r non-atomic vectors}
my_list <- list("Douglas",123,FALSE,42L)
class(my_list)
length(my_list)
```

# Matrices
You can create a matrix using the function matrix
```{r}
my_matrix <- matrix(data=seq(1:9),
       nrow = 3,
       byrow = TRUE)

my_matrix

diag(my_matrix)

```


# Conditions & boolean application
```{r conditions}
# Let's create a vector called marks, which are the student's marks for some test, the marks go from 0 to 100.
marks <- num_vec_ran

# Checking the minimum score
min(marks)

# Checking the maximum score
max(marks)

# Checking the average score
mean(marks)

# Checking the median score
median(marks)

# Checking altogether :)
summary(marks)


# How many students got a score over 70?
over70 <- marks >= 70
class(over70)

# R returns another array, but this time is a boolean array. IT has the same length as marks array.
length(over70)
length(marks)

# It means that for each value on the vector, R returns a TRUE or FALSE argument when the condition was satisfied.
over70

# Booleans are bascically 0 or 1. Where 0 is FALSE and 1 is TRUE. R is smart anough to understand that, so we can run aritimethic operations like sum or mean.

# How many students passed the test with honours?
sum(over70)

# What's the percentage of pass with honours?
mean(over70)
```


# Reading an external dataset into a dataframe
```{r reading an external dataset}
library(foreign)
human_rights <- read.dta(file = "hmnrghts.dta")

class(df)
mode(df)
```

Let's check some data on that dataframe
```{r checking the data}
head(human_rights, 10)
str(df)
summary(df)
```

# Subsetting a dataframe
```{r subsetting}
subset(df, democ > 8)
df[df$democ > 8 & !is.na(df$democ),]
```

# Creating new variables
```{r creating new variables}
df$war <- df$civ_war + df$int_war
head(df)

df$dummy_war <- as.numeric(df$war>0)
head(df)
```

# Dealling with factors
```{r factors}

df$gnpcats <- factor(df$gnpcats)
head(df)
levels(df$gnpcats)

df$gnpcats <- factor(df$gnpcats, levels = c("NA","<1000","1000-1999","2000-2999","3000-3999",">4000"))
levels(df$gnpcats)
summary(df$gnpcats)
```

# Plotting some basic data using ggplot
```{r plotting}
library(ggplot2)

ggplot(df, aes(x=gnpcats)) + 
  geom_bar()
```

```{r adding layers to the plot} 
ggplot(df, aes(x=gnpcats)) + 
  geom_bar(aes(fill=factor(dummy_war)))
```

