---
title: "Image Recovering"
author: "Douglas Zickuhr"
date: "20/8/2018"
output: html_document
---

# Loading libraries
```{r libraries}
library(jpeg)
library(tidyverse)
library(knitr)
library(janitor)
library(corrgram)
library(rpart)
```

# Downloading images
```{r download images}
img_url <- c("http://curso-r.com/img/blog/desafio-recuperacao-img/purple_wave.jpg",
           "http://curso-r.com/img/blog/desafio-recuperacao-img/xadrez_colorido.jpg")
img_name <- basename(img_url)

walk2(img_url,img_name,function(x,y){
  download.file(url = x,
                destfile = y)
})
```

# Reading images using JPEG package into a list
```{r reading images}
images <- map(img_name,readJPEG) %>%
  set_names(janitor::clean_names(img_name))
```


# Checking images dimension
```{r checking dimensions}
map(images,dim)
```

# Converting the jpeg to dataframes
```{r convert jpeg to dataframes}
# Function to generate dataframe from images
generate_df_from_jpeg <- function(img){
  data.frame(
    x = rep(1:dim(img)[2], each = dim(img)[1]),
    y = rep(dim(img)[1]:1, dim(img)[2]),
    r = as.vector(img[,,1]),
    g = as.vector(img[,,2]),
    b = as.vector(img[,,3])
  ) %>% 
    mutate(cor = rgb(r,g,b),
           id = row_number())
}

images_df <- map(images, generate_df_from_jpeg)
```

# Split the dataset into train and test
```{r split dataset into train and test}
# Function to split the dataset into train and test
split_train_test <- function(img) {
  ret <- list()
  
  ret$test <- img %>%
    sample_frac(2/5) %>%
    mutate(b_backup = b,
           b = 0,
           cor = rgb(r, g, b))
  
  ret$train <- img %>% 
    filter(!id%in%ret[1]$id)
  
  ret
}

images_train_test_df <- map(images_df,split_train_test)

```

# Generating a corrgram based on the JPEG images
```{r corrgram}
walk(images_df, function(x) {corrgram::corrgram(x = x)})

```

The first JPEG, purple_wave.jpeg has a very high correlation between the colours and the axis x-y, what suggests a linear relationship. Otherwise, the second JPEG, xadrez_colorido.jpg doesn't have that relatioship.

Something to worry about is the multicolinearity on the linear regression, as long as it seems that the independent values are highly correlated.

# Generating the models with the formula b ~ x + y + r + g values.
```{r modelling}
images_lm <- map(images_train_test_df, ~ lm(formula = b ~ x + y + r + g, data = .$train))
images_cart <- map(images_train_test_df, ~ rpart(formula = b ~ x + y + r + g, data = .$train))
```


# Predicting values based on the models
```{r predictions}
# Function to calculate the prediction
predict_images <- function(x,y){
  predict(x,y$test)
}

images_lm_predictions <- map2(images_lm,images_train_test_df, predict_images)
images_cart_predictions <- map2(images_cart, images_train_test_df, predict_images)
```

Evaluate the linear regression
```{r evaluating linear regression}
map(images_lm,summary)
```

The result of the linear regression for purple_wave.jpg seems very good. We got a Adjusted R-squared of 0.9994. On the other hand, for xadrez_colorido.jpg the result is not so good.


```{r evaluate regression tree}
# Function to calcualte the Mean Absolute Error
MAE <- function(actual, predicted){
  mean(abs(actual$test$b - predicted))
}

map2(images_train_test_df,images_lm_predictions,MAE)

```
Considering that the values are from 0 to 1, the regression tree has a mean difference of 0.17 for xadrez_colorido.jpg, which is way better than the result for purple_wave.jpg  


# Assigning the predicted values to test dataframe.
```{r}
images_train_test_df$purple_wave.jpg$test$b_lm <- images_lm_predictions$purple_wave.jpg
images_train_test_df$purple_wave.jpg$test$b_cart <- images_cart_predictions$purple_wave.jpg
images_train_test_df$xadrez_colorido.jpg$test$b_lm <- images_lm_predictions$xadrez_colorido.jpg
images_train_test_df$xadrez_colorido.jpg$test$b_cart <- images_cart_predictions$xadrez_colorido.jpg


# Function to generate the plot using tidyeval
generate_plot <- function(x, var_name){
  var_name <- enquo(var_name)
  
  # The linear model has predicted some values smaller than 0, which is not accepted by rgb function.
  df <- x$test %>%
  mutate(!!var_name := if_else(!!var_name < 0, 0 , !!var_name),
           cor = rgb(r,g,!!var_name))
  
  # Generating the plot
  ggplot(df) + 
    geom_point(aes(x,y), 
               colour = df$cor)
  
}

```



#Finally, let's visualise the recovered images.

## Linear Regression
```{r plotting images recovered with Linear models}
map(images_train_test_df,generate_plot,var_name = b_lm)
```
Using the predicted values by the Linear Regression, the purple wave was satisfactorily recovered. 
Whilst for "xadrez colorido", the linear model seems to have failed in predict the colour correctly. It's not possible to see any tone of blue on the image.

## Regression Trees - CART
```{r plotting images recovered with regression tree}
map(images_train_test_df,generate_plot,var_name = b_cart)

```

Regarding "purple wave", the values predicted by the CART are also visually good on the prediction but the colours are not smooth as the results from the Linear Regression. 
On the other hand, the CART model predicted satisfactorily the colour tones for "xadrez colorigo".


# Wrapping up
Due to non linear relationship between independent and dependent variables, the image "xadrez colorido" has a better prediction result with the regression tree model.
